Interoception Scale - Data Cleaning

### 2024-12-02 study1/analysis/1_cleaning.qmd
Finished TODO on cleaning and pre-processing scripts

::: panel-tabset

### Summary

@@

**TODO**
- The age plot code should be streamlined (there is no need to compute estimate_density)
- Education: add in the preprocessing a manual reassignment of some of the "Other" manual inputs to our categories (and put Other if not in the categories)
- We can merge the edu and student plot by having student be a "color" aesthethic 
- Make Pie chart for ethnicity (see doggonogo for example). 
- Ethnicity: manually check the others and either assign them to the correct category or put them in "Other"

@@

```{r p_demographics_age_gender}
p_age <- estimate_density(df$Age) |>
  normalize(select = y) |>
  mutate(y = y * 86) |>  # To match the binwidth
  ggplot(aes(x = x)) +
  geom_histogram(data=df, aes(x = Age, fill=Gender), bins=28, position="identity", alpha=0.5) +
  geom_vline(xintercept = mean(df$Age), color = "#ca0020", linewidth=1.5) +
  scale_fill_manual(values = c("Male"= "#64B", "Female"= "#8EB69B", "Other"="orange")) +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(title = "Age and Gender", y = "Number of Participants", color = NULL, subtitle = "Distribution of participants' age and gender") +
  theme_modern(axis.title.space = 10) +
  theme(
    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
    axis.text.y = element_text(size = rel(1.1)),)

@@

```{r p_demographics_education}
#| warning: false

#| error: false

@@

p_edu <- df |>
  ggplot(aes(x = Education)) +
  geom_bar(aes(fill = Education)) +
  scale_y_continuous(expand = c(0, 0), breaks= scales::pretty_breaks()) +
  scale_fill_viridis_d(guide = "none") +
  labs(title = "Education", y = "Number of Participants", subtitle = "Participants per achieved education level") +
  theme_modern(axis.title.space = 15) +
  theme(
    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
    axis.text.y = element_text(size = rel(1.1)),
    axis.text.x = element_text(size = rel(0.5), angle = 45, hjust =1),
    axis.title.x = element_blank()
  )

p_edu

# Student
table(df$Student) |>
  as.data.frame() |>
  rename(Student = Var1, Frequency = Freq) |>
  knitr::kable()
```

@@

```{r p_demographics_ethnicity}
#| warning: false

#| error: false

p_eth <- df |>
  ggplot(aes(x = Ethnicity)) +
  geom_bar(aes(fill = Ethnicity)) +
  scale_y_continuous(expand = c(0, 0), breaks= scales::pretty_breaks()) +
  scale_fill_viridis_d(guide = "none") +
  labs(title = "Ethnicity", y = "Number of Participants", subtitle = "Participants per Ethnicity") +
  theme_modern(axis.title.space = 15) +
  theme(
    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
    axis.text.y = element_text(size = rel(1.1)),
    axis.text.x = element_text(size = rel(0.6), angle = 45, hjust = 1),
    axis.title.x = element_blank())

@@

```{r}
sort(table(df$Country)) |> 
  as.data.frame() |> 
  gt::gt()
```

:::

```{r p_summary}
p_map 
p_age 
p_edu
```

>>>>

::: panel-tabset
### Summary

@@

@@

```{r p_demographics_age_gender}
p_age <- df |>
  ggplot(aes(x = Age, fill = Gender)) + 
  geom_histogram(data=df, aes(x = Age, fill=Gender), binwidth = 2) +
  geom_vline(xintercept = mean(df$Age), color = "red", linewidth=1.5, linetype="dashed") +
  scale_fill_viridis_d() +
  scale_x_continuous(expand = c(0, 0), breaks = seq(20, max(df$Age), by = 10 )) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(title = "Age", y = "Number of Participants", color = NULL, subtitle = "Distribution of participants' age") +
  theme_modern(axis.title.space = 10) +
  theme(
    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
    axis.text.y = element_text(size = rel(1.1)),
    axis.text.x = element_text(size = rel(1.1)),
    axis.title.x = element_blank()
  )

@@

```{r p_demographics_education}
#| warning: false
#| error: false

@@

p_edu <- df |>
  mutate (Student = ifelse(is.na(Student), FALSE, Student)) |>
  ggplot(aes(x = Education)) +
  geom_bar(aes(fill = Student)) +
  scale_y_continuous(expand = c(0, 0), breaks= scales::pretty_breaks()) +
  labs(title = "Education", y = "Number of Participants", subtitle = "Participants per achieved education level", fill = "Is currently a student") +
  theme_modern(axis.title.space = 15) +
  theme(
    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
    axis.text.y = element_text(size = rel(1.1)),
    axis.text.x = element_text(size = rel(0.5), angle = 45, hjust =1),
    axis.title.x = element_blank()
  )

p_edu
```

@@

```{r p_demographics_ethnicity}
#| warning: false
#| error: false

p_eth <- df |> 
  mutate(Ethnicity = case_when(
    Ethnicity == "central Asia" ~ "Central Asian",
    Ethnicity == "American of African descent, Native American and European" ~ "Mixed",
    Ethnicity == "southern european" ~ "White",
    Ethnicity == "persian" ~ "Middle Eastern/North African",
    Ethnicity %in% c("Berber","Native American","Turkish","turkish") ~ "Other",
    TRUE ~ Ethnicity, 
    )) |>
  filter(!is.na(Ethnicity)) |> 
  ggplot(aes(x = "", fill = Ethnicity)) +
  geom_bar() +
  coord_polar("y") +
  theme_minimal() +
  theme(
    axis.text.x = element_blank(),
    axis.title.x = element_blank(),
    axis.text.y = element_blank(),
    axis.title.y = element_blank()
  )

@@

```{r}
sort(table(df$Country)) |> 
  as.data.frame() |> 
  gt::gt()
```
:::

```{r p_summary}

p_map
p_age
p_edu
```
